Analyzing Network Transfer Protocols on a Simulated Interplanetary Internet

### 2024-04-09 paper/paper.tex

In the past decade interest in returning back to space has increased
internationally. Many organizations have started sending remote vehicles into
space for the first time~%\cite{(indian space program, spaceX, ect)}
and there
are talks of a permanent lunar base being created. With an increased amount of
satellites and potentially permanent bases outside of Earths orbit, the demand
on the interplanetary network (IPN) is increased. The IPN has a series of unique
challenges such as a high amount of error, constantly changing network topology,
and long propagation delay. The solution to these problems is implementing a
delay tolerant network. While space organizations have maintained the IPN with a
set of standard protocols, these may not be sufficient for an expanding network.
The simulator proposed shows how an IPN can handle different stages of
development of an IPN as well as increased throughput requirements.

>>>>

In the past decade interest in returning back to space has increased
internationally. Many organizations have started sending remote vehicles into
space for the first time~%\cite{(indian space program, spaceX, ect)}
and there
are talks of a permanent lunar base being created. With an increased amount of
satellites and potentially permanent bases outside of Earths orbit, the demand
on the interplanetary network (IPN) is increased. The IPN has a series of unique
challenges such as a high amount of error, constantly changing network topology,
and long propagation delay. The solution to these problems is implementing a
delay tolerant network. While space organizations have maintained the IPN with a
set of standard protocols, these may not be sufficient for an expanding network.
The simulator proposed shows how an IPN can handle different stages of
development of an IPN as well as increased throughput requirements.
Before these technological changes can be implemented simulations need to be created to 
lower the risk of failure given the high cost of failure. Often satellites will need to be in operation for years 
or even decades. The hardware and software in satellites can often not be updated very well. Thus it will be very 
relevant to investigate these issues well before they are needed.
